%% cv-forge — cover letter template (filled preview: fictional "Michael Scott", 1992)

\documentclass[a4paper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage[english]{babel}
\usepackage[hmargin=1.8cm,vmargin=1.6cm]{geometry}
\usepackage{xcolor}
\usepackage{ragged2e}
\usepackage{microtype}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\urlstyle{same}

\usepackage{CormorantGaramond}
\usepackage{charter}

\definecolor{accentTitle}{HTML}{0E6E55}
\definecolor{accentLine}{HTML}{A16F0B}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

\begin{document}

% ---- Sender header (mirrors the CV) ----------------------------------------
\begin{center}
  {\Huge\color{accentTitle} Michael Gary Scott}\\[10pt]
  {\color{accentLine}\rule{\linewidth}{0.4pt}}\\[6pt]
  \footnotesize
  \faPhone\ +1 (570) 555-0142 \quad\textbullet\quad
  \faMapMarker*\ Scranton, Pennsylvania\\[6pt]
  {\color{accentLine}\rule{\linewidth}{0.4pt}}
\end{center}

\vspace{6pt}

% ---- Date and recipient -----------------------------------------------------
March 2, 1992
\vspace{2pt}

Hiring Manager\\
Dunder Mifflin Paper Company\\
Scranton, Pennsylvania

% ---- Body -------------------------------------------------------------------
\vspace{4pt}
Dear Dunder Mifflin,

\justifying

I am writing to apply for the Sales Representative position at your Scranton branch. Ever
since I can remember, I have loved two things: paper, and people. This is a job where I get
to do both at the same time, and I do not think I have ever wanted anything more.

I believe I would be a great salesman because I genuinely like everyone I meet, and people
can tell. I do not see a customer --- I see a friend I have not sold paper to yet. I am
persistent, I never give up, and I will drive to a client's office in a snowstorm if it
means keeping their business. Give me a phone and a reason, and I will fill an order book.

I know I am starting at the bottom, and that is fine with me. I want to learn everything
about this business, from the smallest ream to the biggest account. One day I would like to
run a branch of my own --- but first I want to be the best salesman you have ever hired, and
the kind of coworker who makes Monday mornings a little less terrible for everybody.

Thank you for reading my letter. I promise you will not regret giving me a chance. I would
love to come in for an interview, meet the team, and show you how much paper one very
motivated person can sell.

\vspace{10pt}
Yours sincerely,\\[6pt]
\textbf{Michael Gary Scott}

\end{document}
