%% cv-forge — ATS-friendly CV template (filled preview: fictional profile "Michael Scott")

\documentclass[a4paper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage[english]{babel}
\usepackage[hmargin=1.6cm,vmargin=1.3cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\urlstyle{same}

% Fonts (serif body, matching the reference style)
\usepackage{CormorantGaramond}
\usepackage{charter}

% ATS readability: map glyphs to Unicode so copy/parse yields real text, not gibberish.
\input{glyphtounicode}
\pdfgentounicode=1

% Accent palette (from the reference style): green title/text, gold rules.
\definecolor{accentTitle}{HTML}{0E6E55}
\definecolor{accentText}{HTML}{0E6E55}
\definecolor{accentLine}{HTML}{A16F0B}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\raggedright

\newcommand{\cvheader}[2]{%
  \begin{center}
    {\Huge\color{accentTitle} #1}\\[9pt]
    {\color{accentLine}\hrule}
    \vspace{4pt}
    \footnotesize #2
    \vspace{4pt}
    {\color{accentLine}\hrule}
  \end{center}
  \vspace{4pt}
}

\titleformat{\section}{\large\bfseries\color{accentText}}{}{0em}{}[\color{accentLine}\titlerule]
\titlespacing{\section}{0pt}{10pt}{4pt}

\newcommand{\entry}[4]{%
  \textbf{#1}\hfill #2\\%
  \textit{#3}\hfill #4\par%
}

\newcommand{\entryline}[2]{\textbf{#1}\hfill #2\par}

\newenvironment{bullets}
  {\begin{itemize}[leftmargin=1.4em,itemsep=1.5pt,topsep=2pt,parsep=0pt]}
  {\end{itemize}}
\renewcommand\labelitemi{--}

\begin{document}

% ---- Header: identity + contact --------------------------------------------
\cvheader{Michael Gary Scott}{%
  Regional Manager \quad\textbullet\quad
  \faEnvelope\ \href{mailto:michael.scott@example.com}{michael.scott@example.com} \quad\textbullet\quad
  \faPhone\ +1 (570) 555-0142 \quad\textbullet\quad
  \faLinkedin\ \href{https://linkedin.com/in/michaelscott}{linkedin.com/in/michaelscott}%
}

% ---- Summary ----------------------------------------------------------------
\section{Summary}
Award-winning Regional Manager and salesman with over 15 years at Dunder Mifflin Paper
Company. Rose from entry-level sales representative to lead the Scranton branch, which he
grew into the company's top-performing region and kept open and profitable through
company-wide consolidation. Founder of the Michael Scott Paper Company, acquired by Dunder
Mifflin within months of launch. Leads through relationships --- with clients he keeps for
decades and with a team he treats as family --- and is happiest closing a sale and making
people laugh in the same afternoon.

% ---- Experience -------------------------------------------------------------
\section{Experience}
\entry{Dunder Mifflin Paper Company}{Scranton, PA}{Regional Manager}{2006 -- Present}
\begin{bullets}
  \item Lead the Scranton branch, consistently the highest-performing sales region in the
    company.
  \item Kept the branch open and growing through company-wide consolidation, absorbing the
    staff and accounts of the closed Stamford office with minimal client loss.
  \item Retained major accounts for years through personal, long-term client relationships
    across the Northeast Pennsylvania paper market.
  \item Built and mentored a sales team that produced several of the company's top
    salespeople.
  \item Founded the annual ``Dundie Awards'' employee-recognition program to drive team
    morale and retention.
\end{bullets}

\vspace{5pt}
\entry{Michael Scott Paper Company}{Scranton, PA}{Founder \& President}{2009}
\begin{bullets}
  \item Founded a paper company from scratch, competing on service and personal attention
    rather than price alone.
  \item Won back key clients so effectively that Dunder Mifflin acquired the company within
    months and reabsorbed its accounts.
\end{bullets}

\vspace{5pt}
\entry{Dunder Mifflin Paper Company}{Scranton, PA}{Sales Representative}{1992 -- 2006}
\begin{bullets}
  \item Consistently a top-performing salesman, earning promotion to Regional Manager.
  \item Grew and retained a personal client base through relentless customer service and
    follow-up.
\end{bullets}

% ---- Key Achievements -------------------------------------------------------
\section{Key Achievements}
\begin{bullets}
  \item Grew the Scranton branch into the highest-performing region in the company.
  \item Founded the Michael Scott Paper Company, acquired by Dunder Mifflin within months
    of launch.
  \item Kept the Scranton branch open through consolidation while other branches closed.
  \item Wrote, produced, directed, and starred in \textit{Threat Level Midnight}, a
    feature-length film completed over 11 years.
\end{bullets}

% ---- Education --------------------------------------------------------------
\section{Education}
\entryline{Sales \& management training --- Dale Carnegie; improv comedy workshops}{}

% ---- Skills -----------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\textwidth}{@{}>{\bfseries}l@{\hspace{12pt}}X@{}}
Sales & prospecting, closing, account retention, client relationships \\
Leadership & team motivation, mentoring, recruiting, conflict resolution \\
Communication & public speaking, presentations, improv comedy, Microsoft PowerPoint \\
Other & event planning, screenwriting, brand of relentless optimism \\
\end{tabularx}

\end{document}
